---
title: "Twitter Analytics - DataONE"
date range: "Beginning-December 2020"
output: html_document
---

```{r setup, echo=FALSE,results=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-packages, echo=FALSE,results=FALSE,message=FALSE}
library(readr)
library(tidyr)
library(knitr)
library(ggplot2)
library(syuzhet)
library(rtweet)
library(dplyr)
library(tidytext)
library(kableExtra)
library(ggraph)
library(formattable)
library(data.table)
library(dendroTools)
library(cowplot)
library(tm)
library(tokenizers)
library(tidyverse)
library(wordcloud)
library(SnowballC)
library(RColorBrewer)
library(wordcloud2)
library(widyr)
library(igraph)
library(topicmodels)
library(DataCombine)
library(ggThemeAssist)
library(quanteda)
library(data.table)
library(lubridate)
library(textclean)
library(gridExtra)
library(grid)
library(lattice)
library(gtable)
library(ggpubr)
```

## DataONE Twitter Metrics

This report contains information about DataONE's Twitter account, @DataONEorg, and how effective it is at engaging a wider audience of data repository professionals, researchers, students, and other data organizations.

```{r manually-gathered-data, echo=FALSE,results=FALSE,message=FALSE}
twitter_summary_metrics <- read_csv("./Raw Dataone/twitter-summary-metrics-d1.csv")
twitter_summary_metrics %>% 
    mutate(Number_Followers = na_if(Number_Followers, "null"))
twitter_summary_metrics$Date <-as.Date(twitter_summary_metrics$Date) 
```

```{r downloaded-scraped-data, echo=FALSE,results=FALSE,message=FALSE}

#establishing twitter api token
#add to your R environment
tw_token <-
rtweet::create_token(
   app =  Sys.getenv('app'),
   consumer_key = Sys.getenv('consumer_key'),
   consumer_secret = Sys.getenv('consumer_secret'),
   access_token = Sys.getenv('access_token'),
   access_secret = Sys.getenv('access_secret'),
  set_renv = TRUE
)

#Getting the timeline of tweets from rtweet
ADC_raw <- get_timeline("@DataONEorg", n= 3200)
ADC_raw$status_id <-as.numeric(ADC_raw$status_id)
ADC_raw <- select(ADC_raw, status_id, created_at, text, display_text_width, reply_to_status_id, reply_to_screen_name,
                  is_retweet, favorite_count, retweet_count, hashtags, media_type, mentions_screen_name)

#If you want to export the tweet timeline as a .csv, run the following commented lines of code.
#ADC <- apply(ADC,2,as.character)
#write.csv(ADC,"/Users/mclean/Downloads/ADC-Tweet-Data.csv", row.names = FALSE)

#Joining rtweet data to downloaded twitter data

files <- list.files("./Raw Dataone/",pattern="tweet_activity_metrics_DataONEorg_",full.names=TRUE)
ADC_downloaded <- lapply(files, read.csv, stringsAsFactors = F)
ADC_downloaded_merge <- do.call(rbind, ADC_downloaded) %>% 
  select(Tweet.id, impressions, engagements, engagement.rate, replies, user.profile.clicks, url.clicks,
         hashtag.clicks, detail.expands, permalink.clicks, media.views, media.engagements)

ADC <- left_join(ADC_raw, ADC_downloaded_merge, by = c("status_id" = "Tweet.id"))
```

```{r making-columns-category, echo=FALSE,results=FALSE,message=FALSE}

#getting rid of any HTML symbols so I don't have things like &amp; in the text of the tweets
ADC$text <-replace_html(ADC$text,symbol=TRUE)

#creating two columns Date AND Time rather than "created at" so that I can subset by Hour or Month
ADC$posdate <- as.POSIXct(ADC$created_at,format="%Y:%m:%d %H:%M:%S")
ADC$posdate <- with_tz(ADC$posdate, tzone = "America/Los_Angeles")
ADC$Time <- format(as.POSIXct(ADC$posdate,format="%Y:%m:%d %H:%M:%S"),"%H:%M:%S")
ADC$Date <- format(as.POSIXct(ADC$posdate,format="%Y:%m:%d %H:%M:%S"),"%Y:%m:%d")
ADC$Hour<-format(strptime(ADC$Time,"%H:%M:%S"),'%H')
ADC$MonthYr<-format(strptime(ADC$Date,"%Y:%m:%d"),'%Y:%m')
ADC$weekday<-wday(as.Date(ADC$Date,"%Y:%m:%d"), label=TRUE)
```

```{r subsetting-by-date, echo=FALSE,results=FALSE,message=FALSE,eval=TRUE}
#use if you want to change the date range of this report

#ADC <- ADC[ADC$Date>="2020:03:11", ] 
ADC <- ADC[ADC$Date<="2020:12:31", ] 

monthlytweets <- ADC %>%  
  group_by(MonthYr) %>%
  summarize(n = n())

monthlytweetsimp <- ADC %>%  
  group_by(MonthYr) %>%
  summarize(impressions_sum = sum(impressions,na.rm=TRUE))

#setwd("~/Documents/Twitter Analytics/Raw Dataone/")
#write.csv(monthlytweetsimp,file='imp_tweet_count.csv')

#removing outlier of 2537 followers gained in May 2017?
twitter_summary_metrics <- twitter_summary_metrics[twitter_summary_metrics$New_Followers<=2500, ] 
```

```{r cleaning-data-organic, echo=FALSE,results=FALSE,message=FALSE,eval=TRUE}
#Creating an organic tweet list

#Remove retweets
ADC_tweets_organic <- ADC[ADC$is_retweet==FALSE, ] 
#Removing that one Sunday tweet
ADC_tweets_organic <- ADC_tweets_organic[ADC_tweets_organic$weekday!="Sun", ] 
# Remove replies
ADC_tweets_organic <- subset(ADC_tweets_organic, is.na(ADC_tweets_organic$reply_to_status_id)) 

#formatting changes for the date and for the list of hashtags
ADC_tweets_organic$created_at <-as.character.Date(ADC_tweets_organic$created_at) 
ADC_tweets_organic$hashtags <- lapply(ADC_tweets_organic$hashtags, paste0, collapse = ", ")
#formatting the variable media type so that I can group by it later on
ADC_tweets_organic$media_type <-unlist(ADC_tweets_organic$media_type,use.names = T)
```



```{r cleaning-data-part-2, echo=FALSE,results=FALSE,message=FALSE}
#summarizing the number of engagements by month
mcount_tweets<-ADC_tweets_organic %>%  
  group_by(MonthYr) %>%
  summarize(n = n())

mcount_engagements<-ADC_tweets_organic %>%  
  group_by(MonthYr) %>%
  summarize(engagement_sum = sum(engagements,na.rm=TRUE))

mcount_impressions<-ADC_tweets_organic %>%  
  group_by(MonthYr) %>%
  summarize(impressions_sum = sum(impressions,na.rm=TRUE))

mcount_retweets<-ADC_tweets_organic %>%  
  group_by(MonthYr) %>%
  summarize(retweets_sum = sum(retweet_count,na.rm=TRUE))

mcount_faves<-ADC_tweets_organic %>%  
  group_by(MonthYr) %>%
  summarize(faves_sum = sum(favorite_count,na.rm=TRUE))

bymonth<-cbind(mcount_tweets,mcount_engagements$engagement_sum,mcount_impressions$impressions_sum, mcount_faves$faves_sum,mcount_retweets$retweets_sum)
names(bymonth)[3] <- "Meng_sum"
names(bymonth)[4] <- "Mimp_sum"
names(bymonth)[5] <- "Mfave_sum"
names(bymonth)[6] <- "Mretweet_sum"

bymonth$year<-substr(bymonth$MonthYr, start = 1, stop = 4)
bymonth$month<-substr(bymonth$MonthYr, start = 6, stop = 7)

bymonth$date<-paste(bymonth$year, bymonth$month, sep="-")
bymonth$date <- as.Date(paste(bymonth$date,"-01",sep=""))

bymonth$normalengagement<-(bymonth$Meng_sum/bymonth$n)
bymonth$normalimpressions<-(bymonth$Mimp_sum/bymonth$n)
bymonth$normalfaves<-(bymonth$Mfave_sum/bymonth$n)
bymonth$normalRTs<-(bymonth$Mretweet_sum/bymonth$n)

#Keeping ONLY the retweets
ADC_retweets <- ADC[ADC$is_retweet==TRUE, ] 

#Keeping ONLY the replies
ADC_replies <- subset(ADC, !is.na(ADC$reply_to_status_id))

```

```{r creating-custom-theme-colors, echo=FALSE,results=FALSE,message=FALSE}
theme_ADC<- function() {
  theme_bw(base_size=12,base_family="Helvetica") %+replace%
    theme(
      plot.title=element_text(size=11, face="bold",margin=margin(10,0,10,0),color="#1D244F"),
      plot.subtitle = element_text(size=10,margin=margin(0,0,10,0),color="#1D244F"),
        axis.text.x = element_text(angle=50, size=8, vjust=0.5, color="#1D244F"),
        axis.text.y = element_text(size=8, color="#1D244F"),
        axis.title.x = element_text(color="#1D244F",vjust=-.5,size=10),
        axis.title.y = element_text(color="#1D244F",angle=90,vjust=.5,size=10),
        panel.background=element_rect(fill="white"),
        axis.line = element_line(color="#1D244F"),
      panel.grid.major = element_line(colour = "white", size = 0.2), 
    panel.grid.minor = element_line(colour = "white", size = 0.5),)
}
ADC_colors <- c(
  `navy`="#1D244E",
  `light blue`="#B3E1E7",
  `green`="#19B369",
  `light green`="#79FD81",
  `teal`="#146660",
  `dark teal`="#1B887E",
  `grey`="#767171",
  `black`="#000000")
```

### How has DataONE's Twitter account increased its reach over time?
These first two graphs illustrate the number of organic Tweets each month (that is, not Retweets or replies, though Retweets with a comment added ARE included) and the number of followers @DataONEorg has gained each month. The number of followers gained does not include any followers lost, and represents the net gain (or loss) of followers.  

The DataONE account currently has `r twitter_summary_metrics$Number_Followers[1]` followers.  

```{r monthly-tweets, echo=FALSE,results=FALSE,message=FALSE, warning=FALSE}
monthlytweets <- ggplot(data = bymonth, aes(x=date, y=n)) +
  geom_point(color="#1B887E",size=2.5)+
  labs(title='Number of Monthly Tweets',
       x="Date",
       y="Number of Tweets")+
  stat_smooth(method="lm", se=FALSE, color="#B3E1E7",size=1)

monthlytweets <- monthlytweets+theme_ADC()
```

```{r followers, echo=FALSE}
followers <- ggplot(data = twitter_summary_metrics, aes(x=Date, y=New_Followers)) +
  geom_point(color="#1B887E",size=2.5)+
  labs(title='Followers Gained Each Month',
       x="Date",
       y="Followers Gained")+
    stat_smooth(method="lm", se=FALSE, color="#B3E1E7",size=1)

followers <- followers+theme_ADC()

```

```{r basic-graphs, echo=FALSE, warning=FALSE}
plot_grid(monthlytweets,followers,
          ncol=2)
```

These next two graphs dig into the metrics associated with each Tweet. Every organic Tweet has a certain number of engagements (that is, the number of times users interact with the Tweet) and impressions (the number of times users are served that Tweet in their timeline). The data presented are normalized on a per Tweet basis because of course there will be more total engagements and impressions as the quantity of Tweets increases.  

```{r normal-impressions-engagements, echo=FALSE}

tweetengagements<-ggplot(data = bymonth, aes(x=date, y=normalengagement)) +
  geom_point(color="#1D244E",size=2.5)+
  labs(title='Engagements per Tweet',
       subtitle = '',
       x="Time",
       y="Engagements per Tweet")+
  stat_smooth(method="lm", se=FALSE, color="#19B369",size=1)

tweetengagements<-tweetengagements+theme_ADC()

tweetimpressions<-ggplot(data = bymonth, aes(x=date, y=normalimpressions)) +
  geom_point(color="#1D244E",size=2.5)+
  labs(title='Impressions per Tweet',
       subtitle = '',
       x="Time",
       y="Impressions per Tweet")+
  stat_smooth(method="lm", se=FALSE, color="#19B369",size=1)

tweetimpressions<-tweetimpressions+theme_ADC()


```
```{r more-depth--graphs, echo=FALSE}
plot_grid(tweetengagements,NULL,tweetimpressions,
          nrow=1,rel_widths = c(1,.15,1))
```
```{r twitter-impressions-tables, echo=FALSE}

ADC_tweets_organic <- ADC_tweets_organic %>% arrange(-engagements)
ADC_tweets_engagements <- select(ADC_tweets_organic,text,created_at, engagements)
ADC_tweets_engagements <- ADC_tweets_engagements[1:5,]

ADC_tweets_organic <- ADC_tweets_organic %>% arrange(-impressions)
ADC_tweets_impressions <- select(ADC_tweets_organic,text,created_at, impressions)
ADC_tweets_impressions <- ADC_tweets_impressions[1:5,]

kable(ADC_tweets_engagements,col.names=c("Tweet","Timestamp","Engagements")) %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE, position = "float_left",font_size=12) %>%
  column_spec(1, width = "18em") %>%
  column_spec(2, width = "6em") %>%
  column_spec(3, width = "4em")

kable(ADC_tweets_impressions,col.names=c("Tweet","Timestamp","Impressions")) %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE, position = "left",font_size=12) %>%
  column_spec(1, width = "18em") %>%
  column_spec(2, width = "6em") %>%
  column_spec(3, width = "4em")
```
The number of engagements includes all actions that a user could take with a Tweet, including Retweeting, clicking anywhere on the Tweet, or favoriting the Tweet. To dig further into those engagements, the following graphs show the number of likes and retweets on a per Tweet basis.  

```{r normal-faves-likes, echo=FALSE}

tweetfaves<-ggplot(data = bymonth, aes(x=date, y=normalfaves)) +
  geom_point(color="#146660",size=2.5)+
  labs(title='Mean Monthly Favorites per Tweet',
       subtitle = '',
       x="Time",
       y="Favorites per Tweet")+
  stat_smooth(method="lm", se=FALSE, color="#79FD81",size=1)

tweetfaves<-tweetfaves+theme_ADC()

tweetRTs<-ggplot(data = bymonth, aes(x=date, y=normalRTs)) +
  geom_point(color="#146660",size=2.5)+
  labs(title='Mean Monthly Retweets per Tweet',
       subtitle = '',
       x="Time",
       y="Retweets")+
  stat_smooth(method="lm", se=FALSE, color="#79FD81",size=1)

tweetRTs<-tweetRTs+theme_ADC()
```
```{r more-engagement-graphs, echo=FALSE}
plot_grid(tweetfaves,NULL,tweetRTs,
          nrow=1,rel_widths = c(1,.15,1))
```
```{r twitter-faves-tables, echo=FALSE}

ADC_tweets_organic <- ADC_tweets_organic %>% arrange(-favorite_count)
ADC_tweets_fav <- select(ADC_tweets_organic,text,created_at,favorite_count)
ADC_tweets_fav <- ADC_tweets_fav[1:5,]

ADC_tweets_organic <- ADC_tweets_organic %>% arrange(-retweet_count)
ADC_tweets_retweets <- select(ADC_tweets_organic,text,created_at, retweet_count)
ADC_tweets_retweets <- ADC_tweets_retweets[1:5,]

kable(ADC_tweets_fav,col.names=c("Tweet","Timestamp","Likes")) %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE, position = "float_left",font_size=12) %>%
  column_spec(1, width = "20em") %>%
  column_spec(2, width = "7em") %>%
  column_spec(3, width = "3em")

kable(ADC_tweets_retweets,col.names=c("Tweet","Timestamp","Retweets")) %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE, position = "left",font_size=12) %>%
  column_spec(1, width = "20em") %>%
  column_spec(2, width = "7em") %>%
  column_spec(3, width = "3em")
```

&nbsp; &nbsp; 
&nbsp; &nbsp; 
&nbsp; &nbsp; 

#### Distribution of replies, retweets, and organic tweets
Analyzing the ratio of replies, retweets and organic tweets can tell you a great deal about the type of account you’re analysing. No one likes a Twitter account that exclusively retweets for instance, without any individual content. Finding a good ratio of replies, retweets and organic tweets is therefore a key metric to monitor if one wishes to improve the performance of an account. 
```{r twitter-ratio, echo=FALSE}

tweet_ratio <- data.frame(
  category=c("Retweets", "Replies", "Organic Tweets"),
  count=c(nrow(ADC_retweets), nrow(ADC_replies), nrow(ADC_tweets_organic))
)

# Adding calculated data columns
tweet_ratio$fraction = tweet_ratio$count / sum(tweet_ratio$count)
tweet_ratio$percentage = tweet_ratio$count / sum(tweet_ratio$count) * 100
tweet_ratio$ymax = cumsum(tweet_ratio$fraction)
tweet_ratio$ymin = c(0, head(tweet_ratio$ymax, n=-1))

#Rounding to two decimal points
tweet_ratio<-round_df(tweet_ratio,2)

#Creating the legend
TweetType<-paste(tweet_ratio$category, tweet_ratio$percentage, "%")

#Plotting the data
ggplot(tweet_ratio,aes(ymax=ymax, ymin=ymin, xmax=4,xmin=3,fill=TweetType))+
  geom_rect()+
  coord_polar(theta="y")+
  xlim(c(2,4))+
  theme_void()+
  theme(legend.position = "right")+ 
  scale_fill_manual(values=c( "#79FDB1","#B4E6EA","#1D244E"))
```



```{r other-account-analysis, echo=FALSE,results=FALSE,warning=FALSE, message=FALSE}

influentialtwitter <- function(account_name, n){
    df <- get_timeline(account_name, n = n)
    df <- select(df, status_id, created_at, text, display_text_width, reply_to_status_id, reply_to_screen_name,
                 is_retweet, favorite_count, retweet_count, hashtags, media_type, mentions_screen_name,followers_count)
    df$mentions_screen_name <- lapply(df$mentions_screen_name, paste0, collapse = ", ") %>% unlist()
    df_results<-filter(df, grepl("arcticdatactr", mentions_screen_name, fixed = TRUE))
    if (nrow(df_results) > 0){
        df_results$account <- account_name
    } else if (nrow(df_results) == 0){
        df_results <- data.frame(account = account_name)
    }
    return(df_results) #always goes at the end of the function
}
accounts<-c("@PolarImpact","@Polar_Research","@PridePolar","@PopePolar","@IARPCCollab","@Toolik" , "@IARC_Alaska","@ArcticResearch","@US_APECS","@DataONEorg", "@EDIgotdata", "@NCEAS", "@USLTER", "@rOpenSci", "@NEON_sci", "@ESA_org", "@ESIPfed")

result_list <- lapply(accounts, influentialtwitter, n = 3200)
result_all <- do.call(bind_rows, result_list)

#orgs that would be influential but haven't tweeted us lol so leave them out for now "@makedatacount", "@thecarpentries","@theAGU","@NSIDC","@MOSAiCArctic","@UArctic","@ArcticCouncil","@GlacierHub",
```

### Engagement with the larger Arctic Research / Policy Community 

One way to understand how impactful our Tweets are is by looking at the influential Twitter accounts that are mentioning @ArcticDataCtr (`r twitter_summary_metrics$Number_Followers[1]` followers) in their Tweets. Influential accounts in the Arctic research space: PolarImpact (`r result_all$followers_count[2]` followers), Polar_Research (`r result_all$followers_count[5]` followers), PridePolar (`r result_all$followers_count[8]` followers), PopePolar (`r result_all$followers_count[9]` followers), IARPCCollab (`r result_all$followers_count[23]` followers), Toolik (`r result_all$followers_count[30]` followers), IARC_Alaska (`r result_all$followers_count[44]` followers), ArcticResearch (`r result_all$followers_count[45]` followers), and US_APECS (`r result_all$followers_count[73]` followers).

Influential accounts in the data repository or open science space: DataONEorg (`r result_all$followers_count[80]` followers), EDIgotdata (`r result_all$followers_count[119]` followers), NCEAS (`r result_all$followers_count[195]` followers), USLTER (`r result_all$followers_count[318]` followers), rOpenSci (`r result_all$followers_count[350]` followers), NEON_sci (`r result_all$followers_count[351]` followers), ESA_org (`r result_all$followers_count[359]` followers), and ESIPfed (`r result_all$followers_count[364]` followers).

```{r other-account-analysis-graphs, echo=FALSE,results=FALSE,warning=FALSE, message=FALSE}
by_account <- result_all %>% group_by(account)

by_account<- by_account %>% summarise(
  total=n(),
  favorite_count = mean(favorite_count),
  retweet_count = mean(retweet_count)
) %>% 
arrange(desc(retweet_count))

#Adding ADC data to table
by_account
ADC_tweets_organicmean <- ADC_tweets_organic %>% summarise(
  favorite_count = mean(favorite_count),
  retweet_count = mean(retweet_count)
)

ADCmetrics<-data.frame("@ArcticDataCtr","NA", ADC_tweets_organicmean$favorite_count[1],ADC_tweets_organicmean$retweet_count[1])
names(ADCmetrics)<-c("account","total","favorite_count","retweet_count")

by_account_ADC<-rbind(by_account,ADCmetrics)
by_account_ADC

by_account_RT<-ggplot(data= by_account_ADC, aes(x=account, y=retweet_count)) +
  geom_col(fill="#B3E1E7")+
  labs(title='Mean Retweets from Influential Accounts',
       x="Account Handle",
       y="Mean Number of Retweets")

by_account_RT<-by_account_RT+theme_ADC()

by_account<- by_account %>% arrange(desc(favorite_count))

by_account_fav<-ggplot(data= by_account_ADC, aes(x=account, y=favorite_count)) +
  geom_col(fill="#79FDB1")+
  labs(title='Mean Favorites from Influential Accounts',
       x="Account Handle",
       y="Mean Number of Favorites")

by_account_fav <-by_account_fav+theme_ADC()

by_account_fav

by_account_ADC_fav<-by_account_ADC %>% arrange(desc(favorite_count))
by_account_ADC_fav
```

This graph illustrates that the Arctic Data Center's organic tweets are favorited often when we are mentioned and/or retweeted by some accounts (eg **`r by_account_ADC_fav$account[1]`** with a mean of `r round(by_account_ADC_fav$favorite_count[1],2)` favorites per tweet, **`r by_account_ADC_fav$account[2]`** with a mean of `r round(by_account_ADC_fav$favorite_count[2],2)` favorites per tweet, and **`r by_account_ADC_fav$account[3]`** with a mean of `r round(by_account_ADC_fav$favorite_count[3],2)` favorites per tweet - compared to a mean of `r round(by_account_ADC_fav$favorite_count[4],2)` favorites on the @ArcticDataCtr account). On the flip side, there are some accounts that when we’re mentioned, the tweets get no favorites at all (eg **`r by_account_ADC_fav$account[16]`** with a mean of `r round(by_account_ADC_fav$favorite_count[16],2)` favorites per tweet, **`r by_account_ADC_fav$account[17]`** with a mean of `r round(by_account_ADC_fav$favorite_count[17],2)` favorites per tweet, and **`r by_account_ADC_fav$account[18]`** with a mean of `r round(by_account_ADC_fav$favorite_count[18],2)` favorites per tweet).

```{r other-account-analysis-graphs2, echo=FALSE,results=FALSE,warning=FALSE, message=FALSE}

by_account_RT

by_account_ADC_rt<-by_account_ADC %>% arrange(desc(retweet_count))
by_account_ADC_rt

twitter_summary_metrics

```


Retweeting is a more direct measure of engagement, as this action puts the ArcticDataCtr name out to a wider variety of followers than just the `r twitter_summary_metrics$Number_Followers[1]` followers we have. This graph illustrates that the Arctic Data Center's organic tweets are retweeted often when we are mentioned and/or retweeted by some accounts (eg **`r by_account_ADC_rt$account[1]`** with a mean of `r round(by_account_ADC_rt$retweet_count[1],2)` retweets per tweet, **`r by_account_ADC_rt$account[2]`** with a mean of `r round(by_account_ADC_rt$retweet_count[2],2)` retweets per tweet, and **`r by_account_ADC_rt$account[3]`** with a mean of `r round(by_account_ADC_rt$retweet_count[3],2)` retweets per tweet - compared to a mean of `r round(by_account_ADC_rt$retweet_count[18],2)` retweets on the @ArcticDataCtr account). On the flip side, there are some accounts that when we’re mentioned, the tweets get fewer retweets (eg **`r by_account_ADC_rt$account[15]`** with a mean of `r round(by_account_ADC_rt$retweet_count[15],2)` retweets per tweet, **`r by_account_ADC_rt$account[16]`** with a mean of `r round(by_account_ADC_rt$retweet_count[16],2)` retweets per tweet, and **`r by_account_ADC_rt$account[17]`** with a mean of `r round(by_account_ADC_rt$retweet_count[17],2)` retweets per tweet).

This graph also shows that tweets from the Arctic Data Center's accounts are getting the fewest retweets as compared to these more influential account - that may be a result of their larger reach in sheer number of followers.

These graphs illustrate places where we should increase our reach - focus on generating content for these influential accounts to favorite and retweet.

### When is the best day and time to post tweets?
Obviously we want to make sure we're tweeting at the right times, so that our community will see and interact with those tweets. Only organic tweets are included in this analysis because engagements and impressions are not calculated the same way for retweets or replies.

#### Does it matter what time the tweets are sent out to the community?  

```{r time-of-day, echo=FALSE,results=FALSE,warning=FALSE, message=FALSE}
#trying to normalize data by number of tweets
count_tweets<-ADC_tweets_organic %>%  
  group_by(Hour) %>%
  summarize(n = n())

count_engagements<-ADC_tweets_organic %>%  
  group_by(Hour) %>%
  summarize(engagement_sum = sum(engagements,na.rm=TRUE))

count_impressions<-ADC_tweets_organic %>%  
  group_by(Hour) %>%
  summarize(impressions_sum = sum(impressions,na.rm=TRUE))

byhour<-cbind(count_tweets,count_engagements$engagement_sum,count_impressions$impressions_sum)
names(byhour)[3] <- "eng_sum"
names(byhour)[4] <- "imp_sum"

byhour$normalengagement<-(byhour$eng_sum/byhour$n)
byhour$normalimpressions<-(byhour$imp_sum/byhour$n)

normal_engagements<-ggplot(data= byhour, aes(x=Hour, y=normalengagement)) +
  geom_col(fill="#156760", color="#79FDB1")+
  labs(title='Timestamp vs Engagements (Normalized)',
       x="Time",
       y="Normalized Engagements")

normal_engagements<-normal_engagements+theme_ADC()

tweettime_engagements<-ggplot(data = ADC_tweets_organic, aes(x=Hour, y=engagements)) +
  geom_col(fill="#156760", color="#79FDB1")+
  labs(title='Timestamp vs Engagements',
       x="Time",
       y="Number of Engagements")

tweettime_engagements<-tweettime_engagements+theme_ADC()

normal_impressions<-ggplot(data= byhour, aes(x=Hour, y=normalimpressions)) +
  geom_col(fill="#79FDB1", color="#156760")+
  labs(title='Timestamp vs Impressions (Normalized)',
       x="Time",
       y="Normalized Impressions")

normal_impressions<-normal_impressions+theme_ADC()

tweettime_impressions<-ggplot(data = ADC_tweets_organic, aes(x=Hour, y=impressions)) +
  geom_col(fill="#79FDB1", color="#156760")+
  labs(title='Timestamp vs Impressions',
       x="Time",
       y="Number of Impressions")

tweettime_impressions<-tweettime_impressions+theme_ADC()

plot_grid(tweettime_engagements,normal_engagements, tweettime_impressions, normal_impressions,
          ncol=2,nrow=2,
          rel_widths = c(1.5,1.5,1.5,1.5))

byhoursortedeng <- byhour %>% arrange(desc(normalengagement))
byhoursortedimp <- byhour %>% arrange(desc(normalimpressions))

```

This analysis suggests it does. Looking at the normalized data (that is, accounting for the number of tweets that have been sent out in each hour bucket), it appears that the top three hours of the day to tweet for the most engagement (in Pacific Time) are `r byhoursortedeng$Hour[1]`:00, `r byhoursortedeng$Hour[2]`:00, and `r byhoursortedeng$Hour[3]`:00. The top three hours of the day to tweet for the most impressions (in Pacific Time) are `r byhoursortedimp$Hour[1]`:00, `r byhoursortedimp$Hour[2]`:00, and `r byhoursortedimp$Hour[3]`:00 - the same as the engagements. It seems quite clear that the times we should be tweeting are those.

#### What about the day of the week?

```{r day-of-week, echo=FALSE,results=FALSE,warning=FALSE,message=FALSE}
#trying to normalize data by number of tweets
count_tweetswk<-ADC_tweets_organic %>%  
  group_by(weekday) %>%
  summarize(n = n())

count_engagementswk<-ADC_tweets_organic %>%   
  group_by(weekday) %>%
  summarize(engagement_sum = sum(engagements,na.rm=TRUE))

count_impressionswk<-ADC_tweets_organic %>%  
  group_by(weekday) %>%
  summarize(impressions_sum = sum(impressions,na.rm=TRUE))

byday<-cbind(count_tweetswk,count_engagementswk$engagement_sum,count_impressionswk$impressions_sum)
names(byday)[3] <- "eng_sum"
names(byday)[4] <- "imp_sum"

byday$normalengagement<-(byday$eng_sum/byday$n)
byday$normalimpressions<-(byday$imp_sum/byday$n)

normal_engagementswk<-ggplot(data= byday, aes(x=weekday, y=normalengagement)) +
  geom_col(fill="#156760", color="#79FDB1")+
  labs(title='Day of Week vs Engagements (Normalized)',
       x="Day of Week",
       y="Normalized Engagements")

normal_engagementswk<-normal_engagementswk+theme_ADC()

tweetday_engagements<-ggplot(data = ADC_tweets_organic, aes(x=weekday, y=engagements)) +
  geom_col(fill="#156760", color="#79FDB1")+
  labs(title='Day of Week vs Engagements',
       x="Day of Week",
       y="Number of Engagements")

tweetday_engagements<-tweetday_engagements+theme_ADC()

normal_impressionswk<-ggplot(data= byday, aes(x=weekday, y=normalimpressions)) +
  geom_col(fill="#79FDB1", color="#156760")+
  labs(title='Day of Week vs Impressions (Normalized)',
       x="Day of Week",
       y="Normalized Impressions")

normal_impressionswk<-normal_impressionswk+theme_ADC()

tweetday_impressions<-ggplot(data = ADC_tweets_organic, aes(x=weekday, y=impressions)) +
  geom_col(fill="#79FDB1", color="#156760")+
  labs(title='Day of Week vs Impressions',
       x="Day of Week",
       y="Number of Impressions")

tweetday_impressions<-tweetday_impressions+theme_ADC()

plot_grid(tweetday_engagements,normal_engagementswk, tweetday_impressions, normal_impressionswk,
          ncol=2,nrow=2,
          rel_widths = c(1.5,1.5,1.5,1.5))

bydaysortedeng <- byday %>% arrange(desc(normalengagement))
bydaysortedimp <- byday %>% arrange(desc(normalimpressions))
```

Looking at the normalized data (that is, accounting for the number of tweets that have been sent out in each hour bucket), it appears that the top two days of the week to tweet for the most engagement are `r bydaysortedeng$weekday[1]` and `r bydaysortedeng$weekday[2]`. The top two days of the week to tweet for the most impressions are `r bydaysortedimp$weekday[1]` and `r bydaysortedimp$weekday[2]` - with Monday overlapping between the two. Previous to this analysis, we were not generating organic content on Mondays - that was a day largely reserved for retweeting (with comment, so it counts in the organic Tweet analysis) content from other accounts. Moving forward, we will Tweet more original content on Mondays, to see if this is an artifact of Retweeting or if Monday is truly the day that our community is most active on Twitter.

### Should we include photos with Tweets or not?

```{r photos, echo=FALSE,results=FALSE,warning=FALSE, message=FALSE}
#trying to normalize data by number of tweets
count_photo_tweets<-ADC_tweets_organic %>%  
  group_by(media_type) %>%
  summarize(n = n())

count_photo_engagements<-ADC_tweets_organic %>%  
  group_by(media_type) %>%
  summarize(engagement_sum = sum(engagements,na.rm=TRUE))

count_photo_impressions<-ADC_tweets_organic %>%  
  group_by(media_type) %>%
  summarize(impressions_sum = sum(impressions,na.rm=TRUE))

photo<-cbind(count_photo_tweets,count_photo_engagements$engagement_sum,count_photo_impressions$impressions_sum)
names(photo)[3] <- "eng_sum"
names(photo)[4] <- "imp_sum"

photo$normalengagement<-(photo$eng_sum/photo$n)
photo$normalimpressions<-(photo$imp_sum/photo$n)

normal_photo_engagements<-ggplot(data= photo, aes(x=media_type, y=normalengagement)) +
  geom_col(fill="#156760", color="#79FDB1")+
  labs(title='Presence of Photos vs Engagements (Normalized)',
       x="Photo Present?",
       y="Normalized Engagements")

normal_photo_engagements<-normal_photo_engagements+theme_ADC()

photo_engagements<-ggplot(data = ADC_tweets_organic, aes(x=media_type, y=engagements)) +
  geom_col(fill="#156760", color="#79FDB1")+
  labs(title='Presence of Photos vs Engagements',
       x="Photo Present?",
       y="Number of Engagements")

photo_engagements<-photo_engagements+theme_ADC()

normal_photo_impressions<-ggplot(data= photo, aes(x=media_type, y=normalimpressions)) +
  geom_col(fill="#79FDB1", color="#156760")+
  labs(title='Presence of Photos vs Impressions (Normalized)',
       x="Photo Present?",
       y="Normalized Impressions")

normal_photo_impressions<-normal_photo_impressions+theme_ADC()

photo_impressions<-ggplot(data = ADC_tweets_organic, aes(x=media_type, y=impressions)) +
  geom_col(fill="#79FDB1", color="#156760")+
  labs(title='Presence of Photos vs Impressions',
       x="Photo Present?",
       y="Number of Impressions")

photo_impressions<-photo_impressions+theme_ADC()

plot_grid(photo_engagements,normal_photo_engagements, photo_impressions, normal_photo_impressions,
          ncol=2,nrow=2,
          rel_widths = c(1.5,1.5,1.5,1.5))

```

### Data Collection - Summary

Data was collected manually on the first of the month from https://analytics.twitter.com/user/dataONEorg/home. In addition to parameters not necessary to this analysis, this summary file contains:

* month: month of Tweet information
* year: year of Tweet information
* tweets: number of Tweets that month
* profile-visits: number of times users visited the @dataONEorg profile page
* new-followers: number of new followers gained (gross new followers; does not account for followers lost)
* tweet-impressions: number of times users are served @dataONEorg tweets in timeline, search results, or from the profile
* mentions: number of times @dataONEorg was mentioned in tweets
* number-followers: number of followers, manually copied from https://twitter.com/dataONEorg. 
    * Number of followers is the only piece of data in this file that is only available from Twitter at the time you access the site i.e. it is not made available with the rest of the data in this dataset. Thus, there are NAs for dates prior to the time I started to collect this data or for dates before I realized this data was ephemeral.

### Data Collection - Monthly Tweets

Data was scraped using the R package rtweet. In addition to parameters not necessary to this analysis, this data contains the following parameters:

* status_id: the identifier for the Tweet, which can be used to find the permanent URL
* created_at: the time the Tweet was sent (GMT)
* text: the text (content) of the Tweet
* display_text_width: how many characters are in the Tweet
* reply_to_status_id: whether the Tweet was a reply
* reply_to_screen_name: who the Tweet was a reply to
* is_retweet: whether the Tweet was a retweet
* favorite_count: number of likes
* retweet_count: number of retweets
* hashtags: what hashtags were used in the Tweet content
* media_type: what type of media was attached to the Tweet
* mentions_screen_name: what other Twitter accounts were mentioned (@) in the Tweet

Additionally, Tweet-level data was also downloaded from https://analytics.twitter.com/user/dataONEorg/home, and in addition to parameters not necessary to this analysis, this data contains the following additional parameters:

* Tweet.id: the identifier for the Tweet, which can be used to find the permanent URL
* impressions: number of times users are served the tweet in timeline, search results, or from the @ArcticDataCtr profile
* engagements: total number of times a user interacted with a Tweet. Clicks anywhere on the Tweet, including Retweets, replies, follows, likes, links, cards, hashtags, embedded media, username, profile photo, or Tweet expansion
* engagement.rate: number of engagements divided by impressions
* replies: number of replies that Tweet generated
* user.profile.clicks: number of times a user clicked on the @ArcticDataCtr profile from that particular tweet
* URL.clicks: number of times that URL within the tweet was clicked
* hashtag.clicks: number of times any of your hashtags were clicked from that tweet
* detail.expands: number of times users clicked 'see more' on your tweet
* permalink.clicks: clicks on the Tweet permalink
* follows: times a user followed you directly from the Tweet
* media.views: number of times media attached to the Tweet is viewed
* media.engagements: an interaction on a tweet that has a piece of media (photo, vine, other video, etc) in it

Data scraped from rtweet and downloaded from the Twitter metrics page were joined based on the Tweet id / status_id variable.
