---
title: "Twitter Analytics - Blueprint MCAT"
date: "Last updated June 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Blueprint MCAT Twitter Metrics

This report contains information about Blueprint MCAT's Twitter account, @Blueprint_MCAT, and how effective it is at engaging a wider audience of pre-med students.

### Data Collection - Summary

Data was collected manually on the first of the month from https://analytics.twitter.com/user/blueprint_mcat/home. This summary file contains:

* month: month of Tweet information
* year: year of Tweet information
* tweets: number of Tweets that month
* profile-visits: number of times users visited the @Blueprint_MCAT profile page
* new-followers: number of new followers gained (gross new followers; does not account for followers lost)
* tweet-impressions: number of times users are served @Blueprint_MCAT tweets in timeline, search results, or from the profile
* mentions: number of times @Blueprint_MCAT was mentioned in tweets

### Data Collection - Monthly Tweets

Data was scraped using the R package rtweet. This data contains the following parameters:

* Tweet ID: the identifier for the Tweet, which can be used to find the permanent URL
* Tweet permalink: permanent URL for the Tweet
* Tweet text: the text (content) of the Tweet
* time: the time the Tweet was sent (GMT)
* impressions: number of times users are served the tweet in timeline, search results, or from the @Blueprint_MCAT profile
* engagements: total number of times a user interacted with a Tweet. Clicks anywhere on the Tweet, including Retweets, replies, follows, likes, links, cards, hashtags, embedded media, username, profile photo, or Tweet expansion
* engagement rate: number of engagements divided by impressions
* retweets: number of times that Tweet was retweeted
* replies: number of replies that Tweet generated
* user profile clicks: number of times a user clicked on the @Blueprint_MCAT profile from that particular tweet
* URL clicks: number of times that URL within the tweet was clicked
* hashtag clicks: number of times any of your hashtags were clicked from that tweet
* detail expands: number of times users clicked 'see more' on your tweet
* permalink clicks: clicks on the Tweet permalink
* follows: times a user followed you directly from the Tweet
* email tweet: number of times the Tweet is shared by email
* media views: number of times media attached to the Tweet is viewed
* media engagements: an interaction on a tweet that has a piece of media (photo, vine, other video, etc) in it

```{r load-packages, echo=FALSE,results=FALSE,message=FALSE}
library(readr)
library(tidyr)
library(knitr)
library(ggplot2)
library(syuzhet)
library(rtweet)
library(dplyr)
library(tidytext)
library(kableExtra)
library(ggraph)
library(formattable)
library(data.table)
library(dendroTools)
library(cowplot)
library(tm)
library(tokenizers)
library(tidyverse)
library(wordcloud)
library(SnowballC)
library(RColorBrewer)
library(wordcloud2)
library(widyr)
library(igraph)
library(topicmodels)
library(DataCombine)
library(ggThemeAssist)
library(quanteda)
library(data.table)
library(lubridate)
library(textclean)
```

```{r raw-data, echo=FALSE,results=FALSE,message=FALSE}
twitter_summary_metrics <- read_csv("~/Documents/Twitter Analytics/Raw Data/twitter-summary-metrics.csv")
twitter_summary_metrics$Date <-as.Date(twitter_summary_metrics$Date) 
```

```{r creating-custom-theme-colors, echo=FALSE,results=FALSE,message=FALSE}
theme_ADC<- function() {
  theme_bw(base_size=12,base_family="Helvetica") %+replace%
    theme(
      plot.title=element_text(size=11, face="bold",margin=margin(10,0,10,0),color="#292929"),
      plot.subtitle = element_text(size=10,margin=margin(0,0,10,0),color="#292929"),
        axis.text.x = element_text(angle=50, size=8, vjust=0.5, color="#292929"),
        axis.text.y = element_text(size=8, color="#292929"),
        axis.title.x = element_text(color="#292929",vjust=-.5,size=10),
        axis.title.y = element_text(color="#292929",angle=90,vjust=.5,size=10),
        panel.background=element_rect(fill="white"),
        axis.line = element_line(color="#292929"),
      panel.grid.major = element_line(colour = "white", size = 0.2), 
    panel.grid.minor = element_line(colour = "white", size = 0.5),
    )
}

ADC_colors <- c(
  `navy`="#2C5191",
  `light blue`="#FED967",
  `green`="#4CA9E1",
  `light green`="#F4BE4F",
  `teal`="#717171",
  `dark teal`="#FFFFFF",
  `grey`="#427BD7",
  `Dgrey`="#292929",
  `Ggrey`="#B7B7B7",
  `black`="#FCAF2D")
```

## Summary Information

```{r monthly-tweets, echo=FALSE,results=FALSE,message=FALSE}
monthlytweets<-ggplot(data = twitter_summary_metrics, aes(x=Date, y=Tweets)) +
  geom_line(color="#156760",size=1.5)+
  labs(title='Monthly Tweets Over Time',
       x="Date",
       y="Tweets")

monthlytweets<-monthlytweets+theme_ADC()
```

```{r followers, echo=FALSE}
followers<-ggplot(data = twitter_summary_metrics, aes(x=Date, y=New_Followers)) +
  geom_line(color="#156760",size=1.5)+
  labs(title='Monthly Followers Over Time',
       x="Date",
       y="Followers")

followers<-followers+theme_ADC()

```

```{r impressions, echo=FALSE}
impressions<-ggplot(data = twitter_summary_metrics, aes(x=Date, y=Tweet_Impressions)) +
  geom_point(color="#156760",size=2.5)+
    labs(title='Monthly Impressions Over Time',
       x="Date",
       y="Impressions")

impressions<-impressions+theme_ADC()
```

```{r tweet-impressions, echo=FALSE}
tweetimpressions<-ggplot(data = twitter_summary_metrics, aes(x=Tweets, y=Tweet_Impressions)) +
  geom_point(color="#156760",size=2.5)+
  labs(title='Impact of Tweets on Impressions',
       x="Tweets",
       y="Impressions")+
  stat_smooth(method="lm", se=FALSE, color="#B4E6EA",size=1)

tweetimpressions<-tweetimpressions+theme_ADC()
```

```{r 4-graphs, echo=FALSE, eval = FALSE}
plot_grid(monthlytweets,followers,impressions,tweetimpressions,
          ncol=2, nrow=2,
          rel_widths = c(1.5,1.5,1.5,1.5))
```

```{r twitter-data, echo=FALSE}
ADC <- get_timeline("@blueprint_mcat", n= 3200)
```

```{r twitter-clean, echo=FALSE}
ADC$text <-replace_html(ADC$text,symbol=TRUE)

#Creating an organic tweet list
#Remove retweets
ADC_tweets_organic <- ADC[ADC$is_retweet==FALSE, ] 
# Remove replies
ADC_tweets_organic <- subset(ADC_tweets_organic, is.na(ADC_tweets_organic$reply_to_status_id)) 
ADC_tweets_organic$created_at <-as.character.Date(ADC_tweets_organic$created_at) 
ADC_tweets_organic$hashtags <- lapply(ADC_tweets_organic$hashtags, paste0, collapse = ", ")

#Keeping ONLY the retweets
ADC_retweets <- ADC[ADC$is_retweet==TRUE, ] 

#Keeping ONLY the replies
ADC_replies <- subset(ADC, !is.na(ADC$reply_to_status_id))
```

#### Top 10: Most Liked Tweets
```{r twitter-faves, echo=FALSE}

ADC_tweets_organic <- ADC_tweets_organic %>% arrange(-favorite_count)
ADC_tweets_fav <- select(ADC_tweets_organic,text,created_at,favorite_count, retweet_count,hashtags)
ADC_tweets_fav <- ADC_tweets_fav[1:10,]

ADC_tweets_fav %>% 
  kable(col.names=c("Tweet","Date and Time","Likes","Retweets", "Hashtags Used")) %>% 
  kable_styling() %>% 
  column_spec(2,width="10em") %>% 
  column_spec(1,width="35em") %>% 
  column_spec(5,width="10em") 

```

#### Top 10: Most Retweeted Tweets
```{r twitter-retweets, echo=FALSE}

ADC_tweets_organic <- ADC_tweets_organic %>% arrange(-retweet_count)
ADC_tweets_retweets <- select(ADC_tweets_organic,text,created_at,favorite_count, retweet_count,hashtags)
ADC_tweets_retweets <- ADC_tweets_retweets[1:10,]

ADC_tweets_retweets %>% 
  kable(col.names=c("Tweet","Date and Time","Likes","Retweets", "Hashtags Used")) %>% 
  kable_styling() %>% 
  column_spec(2,width="10em") %>% 
  column_spec(1,width="35em") %>% 
  column_spec(5,width="10em") 

```

#### Distribution of replies, retweets, and organic tweets
Analyzing the ratio of replies, retweets and organic tweets can tell you a great deal about the type of account you’re analysing. No one likes a Twitter account that exclusively retweets for instance, without any individual content. Finding a good ratio of replies, retweets and organic tweets is therefore a key metric to monitor if one wishes to improve the performance of an account.
```{r twitter-ratio, echo=FALSE}

tweet_ratio <- data.frame(
  category=c("Retweets", "Replies", "Organic Tweets"),
  count=c(nrow(ADC_retweets), nrow(ADC_replies), nrow(ADC_tweets_organic))
)

# Adding calculated data columns
tweet_ratio$fraction = tweet_ratio$count / sum(tweet_ratio$count)
tweet_ratio$percentage = tweet_ratio$count / sum(tweet_ratio$count) * 100
tweet_ratio$ymax = cumsum(tweet_ratio$fraction)
tweet_ratio$ymin = c(0, head(tweet_ratio$ymax, n=-1))

#Rounding to two decimal points
tweet_ratio<-round_df(tweet_ratio,2)

#Creating the legend
TweetType<-paste(tweet_ratio$category, tweet_ratio$percentage, "%")

#Plotting the data
ggplot(tweet_ratio,aes(ymax=ymax, ymin=ymin, xmax=4,xmin=3,fill=TweetType))+
  geom_rect()+
  coord_polar(theta="y")+
  xlim(c(2,4))+
  theme_void()+
  theme(legend.position = "right")+ 
  scale_fill_manual(values=c( "#2C5191","#FED967","#4CA9E1"))
```

### Tweet Text Analysis
Bar graph illustrating the 15 most commonly tweeted words in @Blueprint_MCAT's tweets, with common stop words removed from the list.
```{r text-analysis, echo=FALSE}
#Remove retweets
ADC_tweets_organic <- ADC[ADC$is_retweet==FALSE, ] 
# Remove replies
ADC_tweets_organic <- subset(ADC_tweets_organic, is.na(ADC_tweets_organic$reply_to_status_id)) 

ADC_text_tweets <- ADC_tweets_organic %>%
  select(text) %>%
  unnest_tokens(word, text)

#cleaning organic tweets of any characters we don't want to show in the analysis, like @ or links
ADC_text_tweets$word <-  gsub("https\\S*", "", ADC_text_tweets$word)
ADC_text_tweets$word <-  gsub("@\\S*", "", ADC_text_tweets$word) 
ADC_text_tweets$word  <-  gsub("amp", "", ADC_text_tweets$word) 
#ADC_text_tweets$word  <-  gsub("[\r\n]", "", ADC_text_tweets$word)
#ADC_text_tweets$word  <-  gsub("[:digit:]", "", ADC_text_tweets$word)
#ADC_text_tweets$word  <-  gsub("[:punct:]", "", ADC_text_tweets$word)

#removing stop words from the text

ADC_text_tweets<-as.data.frame(ADC_text_tweets,na.rm=TRUE)
ADC_text_tweets$word<-as.character(ADC_text_tweets$word)

all_stops <- as.data.frame(stopwords("en"))
colnames(all_stops)<- c("word")
all_stops$word<-as.character(all_stops$word)

ADC_text_tweets_cleaned <-ADC_text_tweets[!ADC_text_tweets$word%in%all_stops$word,]

ADC_text_tweets_cleaned<-as.data.frame(table(ADC_text_tweets_cleaned))

ADC_text_tweets_cleaned <- ADC_text_tweets_cleaned %>% arrange(-Freq)
ADC_text_tweets_cleaned <- ADC_text_tweets_cleaned[c(3,5:7,9:13, 16:19,21:22),]

ADC_text_tweets_cleanedgraph<-ADC_text_tweets_cleaned %>% 
  ggplot(aes(x=reorder(ADC_text_tweets_cleaned,Freq),y=Freq))+
  geom_col(fill="#2C5191", color="#FFFFFF")+
  coord_flip() +
  labs(y="Count",
      x="Unique Words",
      title="Top 15 frequently used words in Blueprint MCAT's tweets",
      caption ="Common stop words removed from list.")

ADC_text_tweets_cleanedgraph+theme_ADC()
```

### Showing the most frequently used hashtags
Hashtags used more than 10 times are displayed in the wordcloud below.
```{r hashtags, echo=FALSE, warning=FALSE}
ADC_tweets_organic$hashtags <- as.character(ADC_tweets_organic$hashtags)
ADC_tweets_organic$hashtags <- gsub("c\\(", "", ADC_tweets_organic$hashtags)

set.seed(1234)
wordcloud(ADC_tweets_organic$hashtags, min.freq=10, scale=c(6, .75), random.order=FALSE, rot.per=0.45, 
          colors=ADC_colors)
```

### Understanding what accounts we frequently retweet
Retweeting extensively from one account is usually not what someone looks for in a Twitter account. A helpful insight is therefore to monitor and understand from which accounts most retweets originate. 
Accounts are shown that we have retweeted more than 3 times.
```{r retweet-tracker, echo=FALSE, warning=FALSE}
set.seed(1234)
wordcloud(ADC_retweets$retweet_screen_name, min.freq=3, scale=c(4, .75), random.order=FALSE, rot.per=0.45, 
          colors=ADC_colors)

```

### Understanding the sentiment of tweet content
No one likes a Twitter account that only spreads angry or sad tweets. Capturing the tone of your tweets and how they balance out is a good indication of your account’s performance.

There are short comings as well like conflation deficiency that is the inability to discriminate among different meanings of a word. For example, the word “bat” has at least two distinct meanings: a flying animal, and a piece of sporting equipment. Another challenge is a text may contain multiple sentiments all at once.

Positive and negative are summary values: the positive bar encompasses anticipation, joy, surprise, and trust; the negative bar encompasses anger, disgust, fear, and sadness.
```{r sentiment-tracker, echo=FALSE, warning=FALSE}

# Converting tweets to ASCII to trackle strange characters
ADC_text_tweets <- iconv(ADC_text_tweets, from="UTF-8", to="ASCII", sub="")

#ADC_text_tweets_cleaned<-as.vector(ADC_text_tweets_cleaned["ADC_text_tweets_cleaned"],mode = "character")

ADC_sentiment<-get_nrc_sentiment((ADC_text_tweets),language="english")
ADC_sentimentscores<-data.frame(colSums(ADC_sentiment[,]))

names(ADC_sentimentscores) <- "Score"

ADC_sentimentscores <- cbind("sentiment"=rownames(ADC_sentimentscores),ADC_sentimentscores)
rownames(ADC_sentimentscores) <- NULL

sentiment_graph<-ggplot(data=ADC_sentimentscores[1:8,],aes(x=sentiment,y=Score))+
  geom_bar(aes(fill=sentiment),colour="#2C5191", stat = "identity",)+
  xlab("Sentiments")+ylab("Scores")+
  ggtitle("Total sentiment based on scores")+
  scale_fill_manual(values=c("#2C5191","#292929","#4CA9E1","#FCAF2D","#FED967","#427BD7","#F4BE4F","#B7B7B7"))

aggregated_sentiment_graph<-ggplot(data=ADC_sentimentscores[9:10,],aes(x=sentiment,y=Score))+
  geom_bar(aes(fill=sentiment),colour="#2C5191", stat = "identity",)+
  xlab("Sentiments")+ylab("Scores")+
  ggtitle("Total sentiment based on scores")+
  scale_fill_manual(values=c("#2C5191","#4CA9E1"))

sentiment_graph<-sentiment_graph+theme_ADC()+theme(legend.position="none")
aggregated_sentiment_graph<-aggregated_sentiment_graph+theme_ADC()+theme(legend.position="none")

```

```{r 2-graphs, echo=FALSE}
plot_grid(sentiment_graph,aggregated_sentiment_graph,
          ncol=2, 
          #nrow=2,
          rel_widths = c(5,5))
```
