---
title: "Training-Demographics"
author: "Erin McLean"
date: "12/23/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Training Demographics

This document has visualizations for reporting to NSF on the demographics of the Arctic Data Center's training participants. It is for internal use only.

```{r load-packages, echo=FALSE,results=FALSE,message=FALSE}
library(readr)
library(treemap)
library(tidyr)
library(knitr)
library(ggplot2)
library(syuzhet)
library(rtweet)
library(dplyr)
library(tidytext)
library(kableExtra)
library(ggraph)
library(formattable)
library(data.table)
library(dendroTools)
library(cowplot)
library(tm)
library(tokenizers)
library(tidyverse)
library(wordcloud)
library(SnowballC)
library(RColorBrewer)
library(wordcloud2)
library(widyr)
library(igraph)
library(topicmodels)
library(DataCombine)
library(ggThemeAssist)
library(quanteda)
library(data.table)
library(lubridate)
library(textclean)
library(gridExtra)
library(grid)
library(lattice)
library(gtable)
library(ggpubr)
```
Data was downloaded from the Qualtics platform and imported into a google sheet to aggregate the data.

```{r data, echo=FALSE}
demos <- read_csv("~/Documents/ADC-outreach-git/arctic-data-outreach/Training-Demographics/Training-Demographics.csv")

# figuring out how many total responses we have
total_participants<-nrow(demos)
```

```{r creating-custom-theme-colors, echo=FALSE,results=FALSE,message=FALSE}
theme_ADC<- function() {
  theme_bw(base_size=12,base_family="Helvetica") %+replace%
    theme(
      plot.title=element_text(size=11, face="bold",margin=margin(10,0,10,0),color="#1D244F"),
      plot.subtitle = element_text(size=10,margin=margin(0,0,10,0),color="#1D244F"),
        axis.text.x = element_text(angle=50, size=8, vjust=0.5, color="#1D244F"),
        axis.text.y = element_text(size=8, color="#1D244F"),
        axis.title.x = element_text(color="#1D244F",vjust=-.5,size=10),
        axis.title.y = element_text(color="#1D244F",angle=90,vjust=.5,size=10),
        panel.background=element_rect(fill="white"),
        axis.line = element_line(color="#1D244F"),
      panel.grid.major = element_line(colour = "white", size = 0.2), 
    panel.grid.minor = element_line(colour = "white", size = 0.5),)
}

ADC_colors <- c(
  `navy`="#1D244E",
  `light blue`="#B3E1E7",
  `green`="#19B369",
  `light green`="#79FD81",
  `teal`="#146660",
  `dark teal`="#1B887E",
  `grey`="#767171",
  `black`="#000000")
```

# Visualizations

## What disciplines are folks coming from?
```{r discipline, echo=FALSE}

# seeing how many people are in each category
count_disciplines<-demos %>%  
  group_by(Discipline) %>%
  summarize(n = n())

#setting up parameters for the plot
count_disciplines$percentage = (count_disciplines$n / total_participants) * 100

#Rounding to two decimal points
count_disciplines<-round_df(count_disciplines,2)

#making the lollipop plot
count_disciplines %>%
  arrange(percentage) %>%
  mutate(Discipline=factor(Discipline,Discipline))%>%
  ggplot( aes(x=Discipline, y=percentage) ) +
    geom_segment( aes(x=Discipline ,xend=Discipline, y=0, yend=percentage), color="#1D244E") +
    geom_point(size=3, color="#B3E1E7") +
    coord_flip() +
    theme_ADC() +
    theme(
      panel.grid.minor.y = element_blank(),
      panel.grid.major.y = element_blank(),
      legend.position="none"
    ) +
    xlab("")
```
`r count_disciplines$Discipline[1]` is the most prevalent discipline with `r count_disciplines$percentage[1]`% of participants, with `r count_disciplines$Discipline[2]` and `r count_disciplines$Discipline[3]` in second and third place, with `r count_disciplines$percentage[2]`% and `r count_disciplines$percentage[3]`%, respectively.

## What career stage are folks in when they take advantage of our trainings?
```{r role, echo=FALSE}

# seeing how many people are in each category
count_roles<-demos %>%  
  group_by(Role) %>%
  summarize(n = n())

#setting up parameters for the plot
count_roles$percentage = (count_roles$n / total_participants) * 100

#Rounding to two decimal points
count_roles<-round_df(count_roles,2)

#making labels
count_roles$label <- paste(count_roles$Role, count_roles$percentage, sep = ", ")
count_roles$label <- paste0(count_roles$label, "%")

#making the treemap plot
treemap(count_roles, #Your data frame object
        index=c("label"),  #A list of your categorical variables
        vSize = "percentage",  #This is your quantitative variable
        type="index", #Type sets the organization and color scheme of your treemap
        palette = ADC_colors,  #Select your color palette from the RColorBrewer presets or make your own.
        title="Participants by Role", #Customize your title
        fontsize.title = 14 #Change the font size of the title
        )
```